Are translation equivalents special? Evidence from simulations and empirical data from bilingual infants

### 2021-06-15 paper/paper_TE_bilingual_vocabulary_model.tex
suppressed automatic table numbering

\linenumbers
\usepackage{csquotes}
\usepackage{amsmath}
\renewcommand{\topfraction}{1}
\renewcommand{\bottomfraction}{1}
\renewcommand{\textfraction}{.1}
\renewcommand{\floatpagefraction}{1}
\setcounter{topnumber}{9}
\setcounter{bottomnumber}{9}
\setcounter{totalnumber}{20}
\setcounter{dbltopnumber}{9}
\DeclareUnicodeCharacter{2265}{\ensuremath{\ge}}
\DeclareUnicodeCharacter{2264}{\ensuremath{\le}}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\caption{\label{tab:table1}Summary of the parameters in the Bilingual Vocabulary Model.}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{175px}>{\raggedright\arraybackslash}p{175px}>{\raggedright\arraybackslash}p{175px}}
\toprule
Variable & Definition & Constraints & Relationship.to.other.parameters\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Main Parameters}}\\
\hspace{1em}LEARNABLE & Number of learnable words in each language, given the child’s developmental level & Varies by age. No greater than the number of words on CDI. & Maximum number that could be learned in DOM or NONDOM\\
\hspace{1em}DOM & Words produced in the dominant language & DOM ≥ NONDOM (children always produce more words in dominant than non-dominant language); DOM ≤ LEARNABLE & DOM = (1-BALANCE)×WORD; DOM = WORD - NONDOM\\
\hspace{1em}NONDOM & Words produced in the non-dominant language & NONDOM ≤ DOM (children always produce fewer words in non-dominant than dominant language); NONDOM ≤ LEARNABLE & NONDOM = BALANCE×WORD; NONDOM = WORD - DOM\\
\hspace{1em}BIAS & Bias parameter & BIAS < 1 implies the Avoidance Account; BIAS > 1 implies the Preference Account; BIAS = 1 implies the Neutral Account & \\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Derived Parameters}}\\
\hspace{1em}BALANCE & Balance (relative proportion of words produced in the non-dominant language to the total words produced in both languages) & 0 ≤ BALANCE ≤ .50 (greater values indicate children producing a more similar number of words in their two languages) & BALANCE = NONDOM/WORD; BALANCE = NONDOM/(DOM+NONDOM)\\
\hspace{1em}WORD & Word vocabulary (or total vocabulary size) & W ≤ 2×LEARNABLE (maximum word vocabulary is knowing each word in both languages) & WORD = DOM+NONDOM; WORD = DOM/(1-BALANCE); WORD = NONDOM/(BALANCE)\\
\hspace{1em}TE & Translation equivalents produced &  & TE = BIAS × DOM×NONDOM/LEARNABLE\\
\hspace{1em}CONCEPT & Concept vocabulary (or total conceptual vocabulary size) &  & CONCEPT = WORD - TE; CONCEPT = TE + DOM-SINGLET + NONDOM-SINGLET\\
\hspace{1em}DOM-SINGLET & Singlets in dominant language &  & DOM-SINGLET = DOM - TE\\
\hspace{1em}NONDOM-SINGLET & Singlets in non-dominant language &  & NONDOM\_SINGLET = NONCOM - TE\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{4}{l}{\rule{0pt}{1em}All vocabulary measures are constrained to be integers.}\\
\end{tabular}
\end{table}
\end{landscape}

@@

\caption{\label{tab:table2}Summary of the parameters used in each simulation.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{>{\centering\arraybackslash}p{45px}>{\raggedright\arraybackslash}p{45px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{45px}}
\toprule
Simulation & Learnable words (LEARNABLE) & Words in dominant Language (DOM) & Words in non-dominant language (NONDOM) & Word vocabulary (WORD) & Balance of vocabulary (BALANCE) & Bias parameter (BIAS) & Total number of data points generated\\
\midrule
1 & Constant at 600 & Varied, ranging from 100 to LEARNABLE at an interval of 100 & Varied, ranging from 0 to DOM at an interval of 10 & Calculated as WORD = DOM + NONDOM & Calculated as BALANCE = NONDOM / (DOM+NONDOM) & Constant at 1 & 216\\
2 & Varied at 300, 450, and 600 & Varied, ranging from 100 to LEARNABLE at an interval of 100 & Varied, ranging from 0 to DOM at an interval of 25 & Calculated as WORD = DOM + NONDOM & Calculated as BALANCE = NONDOM / (DOM+NONDOM) & Constant at 1 & 161\\
3 & Varied at 150, 300, 450, and 600 & Varied, ranging from 100 to LEARNABLE at an interval of 100 & Varied, ranging from 0 to DOM at an interval of 25 & Calculated as WORD = DOM + NONDOM & Calculated as BALANCE = NONDOM / (DOM+NONDOM) & Varied at 0.5 (Avoidance Account), 1 (Neutral Account), and 1.5 (Preference Account) & 166\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

@@

\caption{\label{tab:table3}Examples for Simulation 1 of three hypothetical children with different hypothetical word vocabularies (WORD) and vocabulary balance (BALANCE), where the number of learnable words (LEARNABLE) = 600 and BIAS = 1.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{100px}>{\raggedright\arraybackslash}p{140px}>{\raggedright\arraybackslash}p{140px}>{\raggedright\arraybackslash}p{60px}>{\raggedright\arraybackslash}p{60px}>{\raggedright\arraybackslash}p{60px}}
\toprule
Variable & Definition & Calculation & Infant Anne (small vocabulary, unbalanced) & Infant Bernie (small vocabulary, balanced) & Infant Charlie (large vocabulary, balanced)\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Main Parameters}}\\
\hspace{1em}BIAS & Bias parameter &  & 1.0 & 1.0 & 1.0\\
\hspace{1em}LEARNABLE & Learnable words in each language &  & 600.0 & 600.0 & 600.0\\
\hspace{1em}DOM & Words produced in the dominant language &  & 270.0 & 180.0 & 540.0\\
\hspace{1em}NONDOM & Words produced in the non-dominant language &  & 30.0 & 120.0 & 360.0\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Derived Parameters}}\\
\hspace{1em}WORD & Word vocabulary (or total vocabulary size) & DOM + NONDOM & 300.0 & 300.0 & 900.0\\
\hspace{1em}BALANCE & Vocabulary balance & NONDOM / (DOM + NONDOM) & 0.1 & 0.4 & 0.4\\
\hspace{1em}TE & Translation equivalents produced & DOM × NONDOM / LEARNABLE & 13.5 & 36.0 & 324.0\\
\hspace{1em}CONCEPT & Concept vocabulary (or total conceptual vocabulary size) & WORD - TE & 286.5 & 264.0 & 576.0\\
\hspace{1em}DOM-SINGLET & Singlets in dominant language & DOM - TE & 256.5 & 144.0 & 216.0\\
\hspace{1em}NONDOM-SINGLET & Singlets in non-dominant language & NONDOM - TE & 16.5 & 84.0 & 36.0\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

@@

\begin{table}[tbp]

@@

\caption{\label{tab:table4}Demographic characteristics of participants (data points = 229).}

@@

\begin{longtable}{llllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:table5}Pairwise correlations among variables (corrected for multiple comparisons using Benjamini and Yekutieli [2001]).}\\
\toprule
 & \multicolumn{1}{c}{Age (in month)} & \multicolumn{1}{c}{LEARNABLE} & \multicolumn{1}{c}{BALANCE} & \multicolumn{1}{c}{WORD} & \multicolumn{1}{c}{DOM} & \multicolumn{1}{c}{NONDOM} & \multicolumn{1}{c}{TE} & \multicolumn{1}{c}{DOM-SINGLET} & \multicolumn{1}{c}{NONDOM-SINGLET}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:table5} continued}}\\
\toprule
 & \multicolumn{1}{c}{Age (in month)} & \multicolumn{1}{c}{LEARNABLE} & \multicolumn{1}{c}{BALANCE} & \multicolumn{1}{c}{WORD} & \multicolumn{1}{c}{DOM} & \multicolumn{1}{c}{NONDOM} & \multicolumn{1}{c}{TE} & \multicolumn{1}{c}{DOM-SINGLET} & \multicolumn{1}{c}{NONDOM-SINGLET}\\
\midrule
\endhead
Age (in month) &  & 0.95**** & -0.24*** & 0.65**** & 0.69**** & 0.45**** & 0.48**** & 0.65**** & 0.19**\ \\\
LEARNABLE &  &  & -0.23*** & 0.62**** & 0.65**** & 0.43**** & 0.44**** & 0.62**** & 0.21**\ \\\
BALANCE &  &  &  & -0.07\ \ \ \ & -0.29**** & 0.35**** & 0.25**** & -0.58**** & 0.63****\\
WORD &  &  &  &  & 0.96**** & 0.87**** & 0.90**** & 0.74**** & 0.44****\\
DOM &  &  &  &  &  & 0.70**** & 0.76**** & 0.89**** & 0.23***\\
NONDOM &  &  &  &  &  &  & 0.99**** & 0.31**** & 0.72****\\
TE &  &  &  &  &  &  &  & 0.38**** & 0.60****\\
DOM-SINGLET &  &  &  &  &  &  &  &  & -0.09\ \ \ \\\
NONDOM-SINGLET &  &  &  &  &  &  &  &  & \\
CONCEPT &  &  &  &  &  &  &  &  & \\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

\caption{\label{tab:table6}Average number of translation equivalents (TE) produced by each balance group.}
\centering
\begin{tabular}[t]{>{\centering\arraybackslash}p{150px}>{\centering\arraybackslash}p{50px}>{\centering\arraybackslash}p{50px}>{\centering\arraybackslash}p{50px}>{\centering\arraybackslash}p{75px}}
\toprule
  & N & Mean & SD & range\\
\midrule
0.4 < BALANCE ≤ 0.5 & 69 & 92 & 114.44 & 4 - 409\\
0.3 < BALANCE ≤ 0.4 & 58 & 68 & 89.30 & 1 - 376\\
0.2 < BALANCE ≤ 0.3 & 52 & 64 & 57.13 & 5 - 221\\
0.1 < BALANCE ≤ 0.2 & 32 & 47 & 35.17 & 7 - 137\\
0 < BALANCE ≤ 0.1 & 18 & 18 & 11.57 & 2 - 52\\
\bottomrule
\end{tabular}
\end{table}

@@

Prediction Set 2 pertained to expected patterns of acquisition of translation equivalents and singlets for children of different developmental levels. In our dataset, developmental level was approximated by children's age. Figure 3 Panel B shows the concept vocabulary (CONCEPT) of the bilingual children as a function of different ages (a proxy for developmental level), used to estimate the number of LEARNABLE words. To illustrate the acquisition of translation equivalents and singlets at different developmental levels, we divided children into three age groups: younger children of 18--22 months, middle children of 23--27 months, and older children of 28--33 months.

@@

\caption{\label{tab:table7}The number of total English and French productive CDI vocabulary at the 90th percentile at different ages, and the average between the two which serves as the denominator in our computation model.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{>{\centering\arraybackslash}p{75px}>{\centering\arraybackslash}p{125px}>{\centering\arraybackslash}p{125px}>{\centering\arraybackslash}p{125px}}
\toprule
Age (months) & Number of English words produced at 90th percentile & Number of French words produced at 90th percentile & Average (LEARNABLE)\\
\midrule
16 & 129.0 & 97.0 & 113.0\\
17 & 201.5 & 161.1 & 181.3\\
18 & 268.7 & 221.1 & 244.9\\
19 & 330.5 & 277.0 & 303.8\\
20 & 387.0 & 328.8 & 357.9\\
\addlinespace
21 & 438.1 & 376.5 & 407.3\\
22 & 483.8 & 420.0 & 451.9\\
23 & 524.2 & 459.4 & 491.8\\
24 & 559.3 & 494.7 & 527.0\\
25 & 589.0 & 525.9 & 557.4\\
\addlinespace
26 & 613.4 & 553.0 & 583.2\\
27 & 632.4 & 575.9 & 604.1\\
28 & 646.0 & 594.7 & 620.4\\
29 & 654.3 & 609.4 & 631.9\\
30 - 33 & 657.9 & 620.0 & 638.9\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\linenumbers
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage[labelformat=empty]{caption}
\usepackage{caption}
\renewcommand{\topfraction}{1}
\renewcommand{\bottomfraction}{1}
\renewcommand{\textfraction}{.1}
\renewcommand{\floatpagefraction}{1}
\setcounter{topnumber}{9}
\setcounter{bottomnumber}{9}
\setcounter{totalnumber}{20}
\setcounter{dbltopnumber}{9}
\DeclareUnicodeCharacter{2265}{\ensuremath{\ge}}
\DeclareUnicodeCharacter{2264}{\ensuremath{\le}}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\caption{\label{tab:table1}Table 1. Summary of the parameters in the Bilingual Vocabulary Model.}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{175px}>{\raggedright\arraybackslash}p{175px}>{\raggedright\arraybackslash}p{175px}}
\toprule
Variable & Definition & Constraints & Relationship.to.other.parameters\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Main Parameters}}\\
\hspace{1em}LEARNABLE & Number of learnable words in each language, given the child’s developmental level & Varies by age. No greater than the number of words on CDI. & Maximum number that could be learned in DOM or NONDOM\\
\hspace{1em}DOM & Words produced in the dominant language & DOM ≥ NONDOM (children always produce more words in dominant than non-dominant language); DOM ≤ LEARNABLE & DOM = (1-BALANCE)×WORD; DOM = WORD - NONDOM\\
\hspace{1em}NONDOM & Words produced in the non-dominant language & NONDOM ≤ DOM (children always produce fewer words in non-dominant than dominant language); NONDOM ≤ LEARNABLE & NONDOM = BALANCE×WORD; NONDOM = WORD - DOM\\
\hspace{1em}BIAS & Bias parameter & BIAS < 1 implies the Avoidance Account; BIAS > 1 implies the Preference Account; BIAS = 1 implies the Neutral Account & \\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Derived Parameters}}\\
\hspace{1em}BALANCE & Balance (relative proportion of words produced in the non-dominant language to the total words produced in both languages) & 0 ≤ BALANCE ≤ .50 (greater values indicate children producing a more similar number of words in their two languages) & BALANCE = NONDOM/WORD; BALANCE = NONDOM/(DOM+NONDOM)\\
\hspace{1em}WORD & Word vocabulary (or total vocabulary size) & W ≤ 2×LEARNABLE (maximum word vocabulary is knowing each word in both languages) & WORD = DOM+NONDOM; WORD = DOM/(1-BALANCE); WORD = NONDOM/(BALANCE)\\
\hspace{1em}TE & Translation equivalents produced &  & TE = BIAS × DOM×NONDOM/LEARNABLE\\
\hspace{1em}CONCEPT & Concept vocabulary (or total conceptual vocabulary size) &  & CONCEPT = WORD - TE; CONCEPT = TE + DOM-SINGLET + NONDOM-SINGLET\\
\hspace{1em}DOM-SINGLET & Singlets in dominant language &  & DOM-SINGLET = DOM - TE\\
\hspace{1em}NONDOM-SINGLET & Singlets in non-dominant language &  & NONDOM\_SINGLET = NONCOM - TE\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{4}{l}{\rule{0pt}{1em}All vocabulary measures are constrained to be integers.}\\
\end{tabular}
\end{table}
\end{landscape}

@@

\caption{\label{tab:table2}Table 2. Summary of the parameters used in each simulation.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{>{\centering\arraybackslash}p{45px}>{\raggedright\arraybackslash}p{45px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{75px}>{\raggedright\arraybackslash}p{45px}}
\toprule
Simulation & Learnable words (LEARNABLE) & Words in dominant Language (DOM) & Words in non-dominant language (NONDOM) & Word vocabulary (WORD) & Balance of vocabulary (BALANCE) & Bias parameter (BIAS) & Total number of data points generated\\
\midrule
1 & Constant at 600 & Varied, ranging from 100 to LEARNABLE at an interval of 100 & Varied, ranging from 0 to DOM at an interval of 10 & Calculated as WORD = DOM + NONDOM & Calculated as BALANCE = NONDOM / (DOM+NONDOM) & Constant at 1 & 216\\
2 & Varied at 300, 450, and 600 & Varied, ranging from 100 to LEARNABLE at an interval of 100 & Varied, ranging from 0 to DOM at an interval of 25 & Calculated as WORD = DOM + NONDOM & Calculated as BALANCE = NONDOM / (DOM+NONDOM) & Constant at 1 & 161\\
3 & Varied at 150, 300, 450, and 600 & Varied, ranging from 100 to LEARNABLE at an interval of 100 & Varied, ranging from 0 to DOM at an interval of 25 & Calculated as WORD = DOM + NONDOM & Calculated as BALANCE = NONDOM / (DOM+NONDOM) & Varied at 0.5 (Avoidance Account), 1 (Neutral Account), and 1.5 (Preference Account) & 166\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

@@

\caption{\label{tab:table3}Table 3. Examples for Simulation 1 of three hypothetical children with different hypothetical word vocabularies (WORD) and vocabulary balance (BALANCE), where the number of learnable words (LEARNABLE) = 600 and BIAS = 1.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{100px}>{\raggedright\arraybackslash}p{140px}>{\raggedright\arraybackslash}p{140px}>{\raggedright\arraybackslash}p{60px}>{\raggedright\arraybackslash}p{60px}>{\raggedright\arraybackslash}p{60px}}
\toprule
Variable & Definition & Calculation & Infant Anne (small vocabulary, unbalanced) & Infant Bernie (small vocabulary, balanced) & Infant Charlie (large vocabulary, balanced)\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Main Parameters}}\\
\hspace{1em}BIAS & Bias parameter &  & 1.0 & 1.0 & 1.0\\
\hspace{1em}LEARNABLE & Learnable words in each language &  & 600.0 & 600.0 & 600.0\\
\hspace{1em}DOM & Words produced in the dominant language &  & 270.0 & 180.0 & 540.0\\
\hspace{1em}NONDOM & Words produced in the non-dominant language &  & 30.0 & 120.0 & 360.0\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Derived Parameters}}\\
\hspace{1em}WORD & Word vocabulary (or total vocabulary size) & DOM + NONDOM & 300.0 & 300.0 & 900.0\\
\hspace{1em}BALANCE & Vocabulary balance & NONDOM / (DOM + NONDOM) & 0.1 & 0.4 & 0.4\\
\hspace{1em}TE & Translation equivalents produced & DOM × NONDOM / LEARNABLE & 13.5 & 36.0 & 324.0\\
\hspace{1em}CONCEPT & Concept vocabulary (or total conceptual vocabulary size) & WORD - TE & 286.5 & 264.0 & 576.0\\
\hspace{1em}DOM-SINGLET & Singlets in dominant language & DOM - TE & 256.5 & 144.0 & 216.0\\
\hspace{1em}NONDOM-SINGLET & Singlets in non-dominant language & NONDOM - TE & 16.5 & 84.0 & 36.0\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

@@

\begin{table}[h]

@@

\caption{\label{tab:table4}Table 4. Demographic characteristics of participants (data points = 229).}

@@

\begin{longtable}{llllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:table5}Table 5. Pairwise correlations among variables (corrected for multiple comparisons using Benjamini and Yekutieli [2001]).}\\
\toprule
 & \multicolumn{1}{c}{Age (in month)} & \multicolumn{1}{c}{LEARNABLE} & \multicolumn{1}{c}{BALANCE} & \multicolumn{1}{c}{WORD} & \multicolumn{1}{c}{DOM} & \multicolumn{1}{c}{NONDOM} & \multicolumn{1}{c}{TE} & \multicolumn{1}{c}{DOM-SINGLET} & \multicolumn{1}{c}{NONDOM-SINGLET}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:table5} continued}}\\
\toprule
 & \multicolumn{1}{c}{Age (in month)} & \multicolumn{1}{c}{LEARNABLE} & \multicolumn{1}{c}{BALANCE} & \multicolumn{1}{c}{WORD} & \multicolumn{1}{c}{DOM} & \multicolumn{1}{c}{NONDOM} & \multicolumn{1}{c}{TE} & \multicolumn{1}{c}{DOM-SINGLET} & \multicolumn{1}{c}{NONDOM-SINGLET}\\
\midrule
\endhead
Age (in month) &  & 0.95**** & -0.24*** & 0.65**** & 0.69**** & 0.45**** & 0.48**** & 0.65**** & 0.19**\ \\\
LEARNABLE &  &  & -0.23*** & 0.62**** & 0.65**** & 0.43**** & 0.44**** & 0.62**** & 0.21**\ \\\
BALANCE &  &  &  & -0.07\ \ \ \ & -0.29**** & 0.35**** & 0.25**** & -0.58**** & 0.63****\\
WORD &  &  &  &  & 0.96**** & 0.87**** & 0.90**** & 0.74**** & 0.44****\\
DOM &  &  &  &  &  & 0.70**** & 0.76**** & 0.89**** & 0.23***\\
NONDOM &  &  &  &  &  &  & 0.99**** & 0.31**** & 0.72****\\
TE &  &  &  &  &  &  &  & 0.38**** & 0.60****\\
DOM-SINGLET &  &  &  &  &  &  &  &  & -0.09\ \ \ \\\
NONDOM-SINGLET &  &  &  &  &  &  &  &  & \\
CONCEPT &  &  &  &  &  &  &  &  & \\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

\caption{\label{tab:table6}Table 6. Average number of translation equivalents (TE) produced by each balance group.}
\centering
\begin{tabular}[t]{>{\centering\arraybackslash}p{150px}>{\centering\arraybackslash}p{50px}>{\centering\arraybackslash}p{50px}>{\centering\arraybackslash}p{50px}>{\centering\arraybackslash}p{75px}}
\toprule
  & N & Mean & SD & range\\
\midrule
0.4 < BALANCE ≤ 0.5 & 69 & 92 & 114.44 & 4 - 409\\
0.3 < BALANCE ≤ 0.4 & 58 & 68 & 89.30 & 1 - 376\\
0.2 < BALANCE ≤ 0.3 & 52 & 64 & 57.13 & 5 - 221\\
0.1 < BALANCE ≤ 0.2 & 32 & 47 & 35.17 & 7 - 137\\
0 < BALANCE ≤ 0.1 & 18 & 18 & 11.57 & 2 - 52\\
\bottomrule
\end{tabular}
\end{table}

@@

Prediction Set 2 pertained to expected patterns of acquisition of translation equivalents and singlets for children of different developmental levels. In our data set, developmental level was approximated by children's age. Figure 3 Panel B shows the concept vocabulary (CONCEPT) of the bilingual children as a function of different ages (a proxy for developmental level), used to estimate the number of LEARNABLE words. To illustrate the acquisition of translation equivalents and singlets at different developmental levels, we divided children into three age groups: younger children of 18--22 months, middle children of 23--27 months, and older children of 28--33 months.

@@

\caption{\label{tab:table7}Table 7. The number of total English and French productive CDI vocabulary at the 90th percentile at different ages, and the average between the two which serves as the denominator in our computation model.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{>{\centering\arraybackslash}p{75px}>{\centering\arraybackslash}p{125px}>{\centering\arraybackslash}p{125px}>{\centering\arraybackslash}p{125px}}
\toprule
Age (months) & Number of English words produced at 90th percentile & Number of French words produced at 90th percentile & Average (LEARNABLE)\\
\midrule
16 & 129.0 & 97.0 & 113.0\\
17 & 201.5 & 161.1 & 181.3\\
18 & 268.7 & 221.1 & 244.9\\
19 & 330.5 & 277.0 & 303.8\\
20 & 387.0 & 328.8 & 357.9\\
\addlinespace
21 & 438.1 & 376.5 & 407.3\\
22 & 483.8 & 420.0 & 451.9\\
23 & 524.2 & 459.4 & 491.8\\
24 & 559.3 & 494.7 & 527.0\\
25 & 589.0 & 525.9 & 557.4\\
\addlinespace
26 & 613.4 & 553.0 & 583.2\\
27 & 632.4 & 575.9 & 604.1\\
28 & 646.0 & 594.7 & 620.4\\
29 & 654.3 & 609.4 & 631.9\\
30 - 33 & 657.9 & 620.0 & 638.9\\
\bottomrule
\end{tabular}
\end{table}
